Our peculiar motion across the Universe

### 2019-06-26 paper/main.tex
edit

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{ratio_pair_total_ind_total.pdf}
\end{center}
\caption{Ratio}
\label{fig:ratio_total}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{ratio_pair_high_ind_total.pdf}
\end{center}
\caption{Ratio}
\label{fig:ratio_fast}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{ratio_pair_total_ind_total.pdf}
\end{center}
\caption{Ratio of the number of halos in pairs to the total number of isolated
  halos as a function of the cosmological parameters in the abacus
  simulations. Across simulations only $0.9 (\pm 0.2) \%$ of the halos can
  be found in pairs with kinematics and isolation similar to the
  MW-M31 pair.} 
\label{fig:ratio_total}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{ratio_pair_high_ind_total.pdf}
\end{center}
\caption{Ratio of the number of fast halos in pairs to the total
  number of isolated halos as a function of the cosmological
  parameters in the abacus simulations. Only $0.07 (\pm0.02) \%$ of
  the halos have similar kinematic conditions as the MW-M31 pairs.}
\label{fig:ratio_fast}
\end{figure*}
